---
output: 
  md_document:
    variant: markdown_github
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, echo = FALSE}
knitr::opts_chunk$set(
  # echo = FALSE, 
  # warnings = FALSE, 
  # error = FALSE, 
  # message = FALSE,
  collapse = TRUE,
  comment = '#'
)

link_repo <- "https://github.com/PIFSC-Protected-Species-Division/crputils"

```

[![crputils status badge](https://pifsc-protected-species-division.r-universe.dev/badges/crputils)](https://pifsc-protected-species-division.r-universe.dev/crputils)

# crputils
Miscellaneous R utilities used by CRP

What?! It's an R package!!

### Installation

#### R-Universe

##### Binary

```{r, eval = FALSE}
install.packages('crputils', 
                 repos=c('https://pifsc-protected-species-division.r-universe.dev','https://cloud.r-project.org')
)
```

### Source

*You will need a C++ compiler for R*

```{r, eval = FALSE}
install.packages('crputils', type='source', 
                 repos=c('https://pifsc-protected-species-division.r-universe.dev','https://cloud.r-project.org')
)
```

## github

*You will need a C++ compiler for R*

```{r, eval = FALSE}
remotes::install_github('pifsc-protected-species-division/crputils')
```


### Components:

##### Latitude/longitude format conversions

Functions to convert between different latitude/longitude formats. Includes:

- Decimal degrees (DD) TO degrees decimal seconds (DMM) or degrees minutes seconds (DMS)
- Degrees decimal minutes (DMM) TO decimal degrees (DD) or degrees minutes seconds (DMS)
- Degrees minutes seconds (DMS) TO decimal degrees (DD) or degrees decimal minutes (DMM)

See `exampleWorkflows/workflow_latLonCov` for example script to use these functions.

##### GPX creation

Functions to convert tables of lat/lon data to GPX files readable by Coastal Explorer


# Disclaimer

*This software package is developed and maintained by scientists at the NOAA Fisheries Pacific Islands Fisheries Science Center and should be considered a fundamental research communication. The recommendations and conclusions presented here are those of the authors and this software should not be construed as official communication by NMFS, NOAA, or the U.S. Dept. of Commerce. In addition, reference to trade names does not imply endorsement by the National Marine Fisheries Service, NOAA. While the best efforts have been made to insure the highest quality, tools such as this are under constant development and are subject to change.*
